Regularising Lotka--Volterra interaction matrices by species grouping: optimal groupings are unpredictable

### 2022-03-14 article.rnw
Precompute the row and column coclassification matrices as distance matrices in article.rnw.

	#Precalculate distances matrices as well.
	body_weight_distance_matrix <- build_dist_matrix(species_dat$name, species_dat$body_weight, function(w1,w2){abs(w1-w2)})
@

>>>>

	#Precalculate distances matrices as well.
	col_distance_matrix <- 1 - weighted_col_coclassification_matrix
	row_distance_matrix <- 1 - weighted_row_coclassification_matrix
	body_weight_distance_matrix <- build_dist_matrix(species_dat$name, species_dat$body_weight, function(w1,w2){abs(w1-w2)})
@
